Morse Theory

### 2020-11-29 paper.tex
Update paper.tex

All connected non-orientable 2-manifolds without boundary could be expressed as connected sum of  $g$ copies of projective planes $N=P\neq P..\neq P$, where $g$ coincides with the genus of the surface.\\

>>>>

All connected non-orientable 2-manifolds without boundary could be expressed as connected sum of  $g$ copies of projective planes $N=P\# P...\# P$, where $g$ coincides with the genus of the surface.\\
